Liveness-Based Garbage Collection for Lazy Languages

### 2015-06-06 paper/paper.tex
figures in one col.

\begin{figure*}[t!]
%%%%{\color{Myblue}
\begin{picture}(100,130)(0,-90)
%  \begin{center}
    \begin{tabular}{cc}
\begin{boxedminipage}{.42\textwidth}
      {\sf
	\renewcommand{\arraystretch}{1}{
	  \begin{uprogram}
          \UFL\
\UNL{0} (\DEFINE\ (\length\  \pl)
	  \UNL{1}  (\SIF~(\NULLQ \ \pl) $0$
          (\PRIM\ 1\ (\CAR\  \pl))))
           \UNL{0}
	   \UNL{0}  (\DEFINE\ (\append\  \lista\ \listb)
	  \UNL{1}  (\SIF~(\NULLQ \ \lista)
	       \listb
	  \UNL{2} \hspace*{-0.1cm}(\CONS\ (\CAR\  \lista) (\append\
(\CDR\  \lista)
          \listb))))
          \UNL{0}
          \UNL{0} (\LET\ \px\
          $\leftarrow$\ (\CONS\ $5$
%          \UNL{1}\hspace*{1.5cm}
          (\CONS\ (\CONS\ $6$ \NIL) \NIL) \IN
	  \UNL{1} (\LET\ \py\   $\leftarrow$\  (\CONS\ $3$ \NIL) \IN
	  \UNL{2}
          (\LET\ \pz\  $\leftarrow$\  (\append\ \px\  \py)\ \IN\
          \UNL{3} (\SIF~(\NULLQ~(\CAR~(\CDR~\pz)))~$0$~$\pi$:\
(\length\ \pz))))))
	\end{uprogram}
      }}
\end{boxedminipage}
&
\begin{minipage}{.45\textwidth}

\hspace*{1cm}{\epsfig{file=motiv-example.eps, height=4cm}}

\end{minipage}

\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%       &
%%       \raisebox{-25mm}{\scalebox{.75}{
%% 	%%%%%%%%%%%%%%%%%%%%%Uday's stuff%%%%%%%%%%%%%%%%%%%%%%%%%
%%       \psset{unit=1mm}
%%       \psset{linewidth=.3mm}
%%       \begin{pspicture}(0,-5)(70,60)
%% 	%\psframe(0,0)(73,60)
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 	\putnode{o}{origin}{13}{50}{\TwoCells{o1}{o2}}
%% 	\putnode{a}{o}{-10}{-15}{\psframebox{3}}
%% %
%%      \putnode{b}{o}{10}{-15}{\psframebox[linestyle=none,framesep=.5]{\NIL}}
%% 	\ncline[offsetB=-.5,nodesepB=.1]{*->}{o1}{a}
%%
%\aput[-3.5](.5){\scalebox{1.2}{\psframebox[framesep=.2,linestyle=none,
%%      fillstyle=solid,
%% 	%      fillcolor=white]{$\times$}}}
%%
%%  \putnode{b}{o}{0}{-3}{\psframebox[linestyle=none,framesep=.5]{\scalebox
%%{.63}{\nilfigure}}}
%% %	\ncline[offsetB=-.5,nodesepB=.1]{*->}{o2}{b}
%% 	%\ncline[offsetB=-.5,nodesepB=.1]{->}{o2}{b}
%%
%% \putnode{y}{o}{-14}{8}{\psframebox[linestyle=none,framesep=.5]{y}}
%% 	\nccurve[nodesepB=-.2,angleA=330,angleB=120]{->}{y}{o}
%%
%% \aput[-3.5](.5){\scalebox{1.2}{\psframebox[framesep=.2,linestyle=none,
%%fillstyle=solid,
%% 		  fillcolor=white]{$\times$}}}
%% 	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 	\putnode{c}{o}{25}{0}{\TwoCells{c1}{c2}}
%% 	\putnode{d}{c}{10}{-10}{\TwoCells{d1}{d2}}
%% 	\putnode{e}{d}{-13}{-12}{\TwoCells{e1}{e2}}
%% 	\putnode{f}{d}{13}{-12}{\TwoCells{f1}{f2}}
%% 	\ncline[nodesepB=-.5]{*->}{c2}{d}
%% 	\ncline[nodesepB=-.5,linewidth=.7]{->}{c2}{d}
%% 	\nccurve[ncurv=1,angleA=270,angleB=330]{*->}{c1}{a}
%%
%% \aput[-3.5](.2){\scalebox{1.2}{\psframebox[framesep=.2,linestyle=none,
%% fillstyle=solid,
%% 	      fillcolor=white]{$\times$}}}
%% 	\nccurve[nodesepB=-.5,angleA=240,angleB=70]{*->}{d1}{e}
%%
%% \nccurve[nodesepB=-.5,angleA=240,angleB=70,linewidth=.7]{->}{d1}{e}
%% 	\nccurve[nodesepB=-.5,angleA=300,angleB=110]{*->}{d2}{f}
%%
%% \aput[-3.5](.5){\scalebox{1.2}{\psframebox[framesep=.2,linestyle=none,
%% fillstyle=solid,
%% 	      fillcolor=white]{$\times$}}}
%%
%% \putnode{w}{c}{-8}{8}{\psframebox[linestyle=none,framesep=.2]{w}}
%%
%%\putnode{ww}{c}{15}{8}{\psframebox[linestyle=none,framesep=.2]{z}}
%%
%%\nccurve[nodesepB=-.2,angleA=330,angleB=120,linewidth=.7]{->}{w}{c}
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 	\putnode{g}{e}{-8}{-12}{\psframebox{4}}
%% 	\putnode{h}{e}{8}{-14}{\TwoCells{h1}{h2}}
%% 	\putnode{i}{f}{-8}{-11}{\psframebox{6}}
%% %
%%\putnode{j}{f}{8}{-11}{\psframebox[linestyle=none,framesep=.5]{\NIL}}
%% 	\ncline[offsetB=-.5,nodesepB=.1]{*-}{e1}{e1}
%%
%%\ncline[linestyle=dashed,offsetB=-.5,nodesepB=.1,linewidth=.7]{->}{e1}{g}
%%         %here
%%
%%\putnode{j1}{f}{0}{-3}{\psframebox[linestyle=none,framesep=0]{\scalebox{.63}{\nilfigure}}}
%%
%%\putnode{j2}{h}{0}{-3}{\psframebox[linestyle=none,framesep=.5]{
%%\scalebox{.63}{\nilfigure}}}

%% %
%%\aput[-3.2](.6){\scalebox{1.2}{\psframebox[framesep=.1,linestyle=none,
%%fillstyle=solid,
%% %	      fillcolor=white]{$\times$}}} %and here
%% 	\ncline[offsetB=-.5,nodesepB=-.3]{*-}{e2}{e2}
%%
%%\ncline[linestyle=dashed,offsetB=-.5,nodesepB=.1,linewidth=.7]{->}{e2}{h}
%% %
%%\aput[-3.2](.5){\scalebox{1.2}{\psframebox[framesep=.1,linestyle=none,
%%fillstyle=solid,
%% %	      fillcolor=white]{$\times$}}} %and here

%% 	\ncline[offsetB=-.5,nodesepB=.1]{*->}{f1}{i}
%% 	\ncline[offsetB=-.5,nodesepB=.1]{*->}{f2}{j}
%% 	\nccurve[nodesepB=-.2,angleA=270,angleB=90]{->}{ww}{d}
%%
%%\aput[-3.2](.4){\scalebox{1.2}{\psframebox[framesep=.1,linestyle=none,fillstyle=solid,
%% 	      fillcolor=white]{$\times$}}}
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 	\putnode{k}{h}{-8}{-11}{\psframebox{5}}
%% %
%%\putnode{l}{h}{8}{-11}{\psframebox[linestyle=none,framesep=.5]{\NIL}}
%% 	\ncline[offsetB=-.5,nodesepB=.1]{*-}{h1}{h1}
%%
%%\ncline[linestyle=dashed,offsetB=-.5,nodesepB=.1,linewidth=.7]{->}{h1}{k}
%% %	\ncline[offsetB=-.5,nodesepB=.1]{*->}{h2}{l}
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        %%
%%       \end{pspicture}}} \\
%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

      (a) Example program.&\hspace*{2cm}
      \renewcommand{\arraystretch}{.9}{\begin{tabular}[t]{ll}
	(b) Memory graph at $\pi$. Thick edges denote  \\
        {\white (b) }live links. Traversal stops at edges marked\\
        {\white (b) }$\times$  during garbage collection.
      \end{tabular}}
    \end{tabular}
\end{picture}

\kern -3ex

\caption{Example Program and its Memory Graph.{\color{red}Amey will combine this with the figure for syntax}}\label{fig:mot-example}
\end{figure*}

@@

\begin{figure*}[]
\footnotesize
\begin{eqnarray*}
   p \in \mathit{Prog} & ::= & d_1 \ldots d_n \,\, e_\mainpgm
    \hspace{7em} \mbox{\em --- program}\\
    \mathit{df} \in Fdef & ::= & (\DEFINE\,\, (f\,\, x_1 \,\, \ldots \,\,x_n)\,\,
    e) 
    \hspace{2.2em} \ \ \ \ \mbox{\em --- function definition} \\
e \in \mathit{Expr} & ::= &
\left\{\begin{array}{ll@{\hspace{4em}}l}
       (\SIF\,\, x\,\, e_1\,\, e_2) && \!\!\!\mbox{\em --- conditional} \\
       (\LET\,\, x \leftarrow s\,\, \IN\,\, e) &&\!\!\! \mbox{\em --- let
binding} \\
       (\SRETURN\,\, x) && \!\!\!\mbox{\em --- return from function}
    \end{array}\right. \\
s \in \mathit{Application} & ::= &
\left\{\begin{array}{lr@{\hspace{1em}}l}
       k && \mbox{\em --- constant (numeric or $\NIL$)}\\
       (\CONS\,\, x_1\,\, x_2) && \mbox{\em --- constructor} \\
       (\CAR\,\, x) &  (\CDR\,\, x) & \mbox{\em --- selectors} \\
       (\NULLQ\,\, x) & (\PRIM\,\, x_1\,\, x_2) & \mbox{\em ---  tester
and generic arithmetic} \\
%        (\NULLQ\,\, x) && \mbox{\em ---  tester} \\
       (\ID\,\, x) && \mbox{\em ---  identity function (for inlining)}
\\
%        (\PRIM\,\, x_1\,\, x_2) && \mbox{\em --- generic arithmetic}
\\
       \multicolumn{2}{l}{(f\,\, x_1\,\,\ldots\,\, x_n)}
            & \mbox{\em --- function application}
    \end{array}\right.
\end{eqnarray*}
  \caption{The syntax of our language}\label{fig:lang-syntax}
\figrule
\normalsize
\end{figure*}

>>>>

\begin{figure}[t!]
  %%%%{\color{Myblue}
  \psset{unit=1mm}
  \begin{pspicture}(80,50)(0,-50)
    %\psframe(80,50)(0,-50)
    %  \begin{center}
    \begin{tabular}{@{}c@{}}
      \begin{boxedminipage}{.42\textwidth}
        {\sf
	  \renewcommand{\arraystretch}{1}{
	    \begin{uprogram}
              \UFL\
              \UNL{0} (\DEFINE\ (\length\  \pl)
	      \UNL{1}  (\SIF~(\NULLQ \ \pl) $0$
              (\PRIM\ 1\ (\CAR\  \pl))))
              \UNL{0}
	      \UNL{0}  (\DEFINE\ (\append\  \lista\ \listb)
	      \UNL{1}  (\SIF~(\NULLQ \ \lista)
	      \listb
	      \UNL{2} \hspace*{-0.1cm}(\CONS\ (\CAR\  \lista) (\append\
              (\CDR\  \lista)
              \listb))))
              \UNL{0}
              \UNL{0} (\LET\ \px\
              $\leftarrow$\ (\CONS\ $5$
              %          \UNL{1}\hspace*{1.5cm}
              (\CONS\ (\CONS\ $6$ \NIL) \NIL) \IN
	      \UNL{1} (\LET\ \py\   $\leftarrow$\  (\CONS\ $3$ \NIL) \IN
	      \UNL{2}
              (\LET\ \pz\  $\leftarrow$\  (\append\ \px\  \py)\ \IN\
              \UNL{3} (\SIF~(\NULLQ~(\CAR~(\CDR~\pz)))~$0$~$\pi$:\
              (\length\ \pz))))))
	    \end{uprogram}
        }}
      \end{boxedminipage}
      \\
      (a) Example program. \\ \\
      \begin{minipage}{.45\textwidth}
        %\hspace*{1cm}
                {\epsfig{file=motiv-example.eps, height=4cm}}
      \end{minipage}
      \\ \renewcommand{\arraystretch}{.9}{\begin{tabular}[t]{ll}
          (b) Memory graph at $\pi$. Thick edges denote live
          links. Traversal \\{\white (b)} stops at edges
          marked $\times$ during garbage collection.
      \end{tabular}}
    \end{tabular}
  \end{pspicture}
 \vspace*{-3ex}
  \caption{Example Program and its Memory Graph}\label{fig:mot-example}
\end{figure}

@@

\begin{figure}[t]
\footnotesize
\begin{eqnarray*}
   p \in \mathit{Prog} & ::= & d_1 \ldots d_n \,\, e_\mainpgm
    \hspace{5em} \mbox{\em --- program}\\
    \mathit{df} \in Fdef & ::= & (\DEFINE\,\, (f\,\, x_1 \,\, \ldots \,\,x_n)\,\,
    e) 
    \hspace{0.2em} \ \ \ \ \mbox{\em --- function definition} \\
e \in \mathit{Expr} & ::= &
\left\{\begin{array}{@{}ll@{\hspace{2em}}l}
       (\SIF\,\, x\,\, e_1\,\, e_2) && \!\!\!\mbox{\em --- conditional} \\
       (\LET\,\, x \leftarrow s\,\, \IN\,\, e) &&\!\!\! \mbox{\em --- let
binding} \\
       (\SRETURN\,\, x) && \!\!\!\mbox{\em --- return from function}
    \end{array}\right. \\
s \in \mathit{Application} & ::= &
\left\{\begin{array}{@{}l@{\hspace{1.2em}}l}
       k & \mbox{\em --- constant (numeric or $\NIL$)}\\
       (\CONS\,\, x_1\,\, x_2) & \mbox{\em --- constructor} \\
       (\CAR\,\, x) & \\ 
       (\CDR\,\, x) & \mbox{\em --- selectors} \\
       (\NULLQ\,\, x) & \\ 
       (\PRIM\,\, x_1\,\, x_2) & \mbox{\em ---  tester
and generic arithmetic} \\
       (\ID\,\, x) & \mbox{\em ---  identity function (for inlining)} \\
\\
       (f\,\, x_1\,\,\ldots\,\, x_n) & \mbox{\em --- function application}
    \end{array}\right.
\end{eqnarray*}
  \caption{The syntax of our language}\label{fig:lang-syntax}
\figrule
\normalsize
\end{figure}
